A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2018-02-04 paper.tex
updated figures and results discussion

\begin{table}[]
\centering
\caption{Key Parameters for Deciding Harmonization Methods for \noxx Emissions in the Energy Sector in Asia}
\label{tab:nox}
\begin{tabular}{|p{1.2cm}|p{.5cm}|p{.5cm}|p{4.5cm}|p{3cm}|}
\hline
\textbf{Region} & \textbf{dH} & $\mathbf{c_v}$ & \textbf{Decision Tree Traversal (Branch and Direction)} & \textbf{Default Method Chosen} \\ \hline
    \hline
CPA             & 0.35        & 2.26          & 1 (no), 2 (no), 3 (yes)                                 & reduce\_ratio\_2080    \\ \hline
PAS             & 0.14        & 1.24          & 1 (no), 2 (no), 3 (yes)                                 & reduce\_ratio\_2080    \\ \hline
SAS             & 0.56        & 0.58          & 1 (no), 2 (no), 3 (no), 4 (no)                          & constant\_ratio        \\ \hline
\end{tabular}
\end{table}

@@

Figure \ref{fig:co} presents a case in which the magnitude of a trajectory is
distorted. A large discrepancy ($\sim$300\% relative difference) is observed in
the harmonization year for carbon monoxide (CO) emissions in the industrial
sector specifically for the South Asia (SAS) MESSAGE-GLOBIOM region, which
comprises most of the emissions of the Asian subcontinent. The default method
chosen (\code{constant_ratio}) maintains model trends for the region; however,
overall model results are distorted. By applying a \code{constant_offset}
override, the regional trend and magnitude is maintained. With the new
harmonization method for the SAS region, the global trajectory for industrial CO
also is representative of the trends seen in the unharmonized trajectory and the
relative importance of the underlying regional trajectories is maintained.

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{results_CO_Industrial_Sector.pdf}
    \caption[]{
      \label{fig:co}
      CO Industrial Sector harmonized and unharmonized emissions are presented
      for SSP2 and SSP2-45 scenarios. Scenarios as denoted identically to Figure
      \ref{fig:nox}. Panels \textbf{a} and \textbf{b} show harmonized and
      overridden-harmonized (respectively) regional trajectories for the 3
      MESSAGE-GLOBIOM regions that comprise the R5ASIA region: Centrally Planned
      Asia (CPA), Other Pacific Asia (PAS), and South Asia (SAS). Notably, the
      SAS regional trajectory displays a distorted trajectory due to the
      harmonization-year difference between history and model results in both
      scenarios. The distortion is large enough to affect global results, as
      shown in Panels \textbf{c} and \textbf{d}.  
}
  \end{center}
\end{figure}

In certain circumstances, the application of the default harmonization methods
can affect not only the magnitude but also the shape of regional
trajectories. Figure \ref{fig:nh3} shows an example case of emissions
trajectories for ammonia (\nht) from the agriculture sector in Asia. Again, the
SAS region shows a large discrepancy in the harmonization year ($>$150\% in this
case). The resulting trajectory harmonized with the default method
(\code{constant_ratio}) provides a large increase after 2080 in the SSP2
reference scenario. Notably, the SSP2-45 scenario is not affected to the same
degree. While this distortion changes the magnitude of the SAS trajectory, it
largely affects the post-2080 shape of the global trajectory (see Figure
\ref{fig:nh3}, panel \textbf{c}). By using a \code{constant_offset} method as an
override, this distortion is addressed and more accurately reflects unharmonized
results in the SAS region, the relative importance between regions, and global
results for agricultural ammonia emissions, each of which contributes to a
better harmonization quality for the harmonized SAS trajectory.

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{results_NH3_Agriculture.pdf}
    \caption[]{
      \label{fig:nh3}
      \nhtt agricultural harmonized and unharmonized emissions are presented for
      SSP2 and SSP2-45 scenarios. Scenarios and panel layouts are identical to
      Figure \ref{fig:co}. In this case, the SAS trajectory again shows not only
      a magnitude distortion, but also a shape distortion at the tail of the
      trajectory. Additionally, global trajectories are greatly affected by the
      harmonization method choice (there is $\sim$20\% relative difference
      between trajectories in the reference scenario in 2100). Override methods
      have been applied to correct the distortion.  }
  \end{center}
\end{figure}

>>>>

\begin{table}[]
\centering
\caption{Key Parameters for Deciding Harmonization Methods for \noxx Emissions in the Energy Sector in Asia}
\label{tab:nox}
\begin{tabular}{|p{1.2cm}|p{.5cm}|p{.5cm}|p{4.5cm}|p{3cm}|}
\hline
\textbf{Region} & \textbf{dH} & $\mathbf{c_v}$ & \textbf{Decision Tree Traversal (Branch and Direction)} & \textbf{Default Method Chosen} \\ \hline
    \hline
\gls{cpa}             & 0.35        & 2.26          & 1 (no), 2 (no), 3 (yes)                                 & reduce\_ratio\_2080    \\ \hline
\gls{pas}             & 0.14        & 1.24          & 1 (no), 2 (no), 3 (yes)                                 & reduce\_ratio\_2080    \\ \hline
\gls{sas}             & 0.56        & 0.58          & 1 (no), 2 (no), 3 (no), 4 (no)                          & constant\_ratio        \\ \hline
\end{tabular}
\end{table}

@@

Figure \ref{fig:co} presents a case in which the magnitude of a trajectory is
distorted. A large discrepancy ($\sim$300\% relative difference) is observed in
the harmonization year for carbon monoxide (CO) emissions in the industrial
sector specifically for the \gls{sas} and \gls{afr} MESSAGE-GLOBIOM
regions. Furthermore, emissions in both regions see relatively large expansion
or contraction, depending on the scenario; therefore, both regions are
candidates for choosing harmonization method overrides. The default method
chosen in both cases (\code{constant_ratio}) maintains model trends for the
region; however, overall model results are distorted. By applying a
\code{constant_offset} overrides, the regional trends and magnitudes are
maintained. Through the use of harmonization overrides also ameliorates issues
seen in the harmonized global trajectory of industrial CO (Figure \ref{fig:co},
Panel \textbf{c}). Not only does the global trajectory with overrides more
accurately match the original unharmonized model behavior and magnitude of
emissions, but the relative importance of the underlying regional trajectories
is also maintained.

\begin{figure}
  \begin{center}
    \includegraphics[height=0.8\textheight]{sep_regions_results_CO_Industrial_Sector.pdf}
    \caption[]{
      \label{fig:co}
      CO Industrial Sector harmonized (without markers) and unharmonized (with
      markers) emissions are presented for SSP2 (purple lines) and SSP2-45 (red
      lines) scenarios. Panel \textbf{a} shows harmonized and
      overridden-harmonized (respectively) trajectories for the \gls{sas} region
      while panels \textbf{b} and \textbf{c} show similar trajectories for the
      \gls{afr} region and (total) global emissions, respectively. Notably, the
      \gls{sas} and \gls{afr} regional trajectory displays a distorted
      trajectory due to the harmonization-year difference between history and
      model results in both scenarios. The distortion is large enough to affect
      global results, as shown in Panel \textbf{c}.  }
  \end{center}
\end{figure}

In certain circumstances, the application of the default harmonization methods
can affect not only the magnitude but also the shape of regional
trajectories. Figure \ref{fig:nh3} shows an example case of emissions
trajectories for ammonia (\nht) from the agriculture sector. Again, the
\gls{sas} region shows a large discrepancy in the harmonization year ($>$150\%
in this case). The resulting trajectory harmonized with the default method
(\code{constant_ratio}) provides a large increase after 2080 in the SSP2
reference scenario. Notably, the SSP2-45 scenario is not affected to the same
degree. While this distortion changes the magnitude of the \gls{sas} trajectory,
it largely affects the post-2080 shape of the global trajectory (Figure
\ref{fig:nh3}, Panel \textbf{b}). For example, in the original model result,
\gls{SAS} \nht agricultural emissions contribute $\sim$30\% of total global
emissions, whereas in the unharmonized case with default methods, \gls{SAS}
comprises $\sim$50\% of global emissions. By using a \code{constant_offset}
method as an override, this distortion is addressed and more accurately reflects
unharmonized results in the \gls{sas} region, the relative importance between
regions, and global results for agricultural ammonia emissions, each of which
contributes to a better harmonization quality for the harmonized \gls{sas}
trajectory. The harmonized emissions using overrides result in a contribution of
$\sim$32\% of total global emissions by the \gls{SAS} region which aligns
closely with the unharmonized model results.

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{sep_regions_results_NH3_Agriculture.pdf}
    \caption[]{
      \label{fig:nh3}
      \nhtt agricultural harmonized and unharmonized emissions are presented for
      SSP2 and SSP2-45 scenarios. Panel \textbf{a} shows harmonized and
      overridden-harmonized (respectively) trajectories for the \gls{sas}
      region, and panel \textbf{b} shows the global total trajectory. In this
      case, the \gls{sas} trajectory again shows not only a magnitude distortion, but
      also a shape distortion at the tail of the trajectory. Additionally,
      global trajectories are greatly affected by the harmonization method
      choice (there is $\sim$20\% relative difference between trajectories in
      the reference scenario in 2100). Override methods have been applied to
      correct the distortion.  }
  \end{center}
\end{figure}
